---
title: "Essentials of Data Analytics"
author: "19BCE1395-Trishit Chakraborty"
date: "1/25/2022"
output:
  word_document: default
  html_document: default
subtitle: Ex-2
---

Consider 25 observations from in the given dataframe titled ‘data’, store first 5
observations (6:00-08:00 ) in ‘data1’, next 10 observations(8:30-13:00) in ‘data2’ and
the last 11 observations (13:00-18:00) in ‘data3’. Perform the following using R
Programming - 

##### Reading the dataset

```{r, echo=TRUE}
data = read.csv("data.csv")
head(data)
View(data)
```


##### rbind (data1, data2) 

```{r, echo=TRUE}
data1 = data[1:5, ]
data1
data2 = data[6:15, ]
data2 
data3 = data[15:25, ]
data3
rbind(data1, data2)
```

##### Store LCZ(TT=0), LCZ(TT=3), LCZ(TT=5), in variables V1, V2 and V3 respectively.
##### Cbind all these three columns

```{r, echo=TRUE}
v1 = data$LCZ0
v2 = data$LCZ3
v3 = data$LCZ5
cbind(v1, v2, v3)
```

#####  Plot Time Vs Pyranometer reading of ‘data’

```{r, echo=TRUE}
attach(data)
library(ggplot2)
p<-ggplot(data=data, aes(x=ï..Time, y=Pyranometer)) +
  geom_bar(stat="identity")
p
```

#####  Plot Pyranometer reading Vs Two 

```{r, echo=TRUE}
attach(data)
p1<-ggplot(data=data, aes(x=Two_0, y=Pyranometer)) +
  geom_bar(stat="identity")
p1

p2<-ggplot(data=data, aes(x=Two_3, y=Pyranometer)) +
  geom_bar(stat="identity")
p2

p3<-ggplot(data=data, aes(x=Two_5, y=Pyranometer)) +
  geom_bar(stat="identity")
p3
```

##### Plot Pyranometer reading Vs Qact

```{r, echo=TRUE}
p1<-ggplot(data=data, aes(x=Quact_0, y=Pyranometer)) +
  geom_bar(stat="identity")
p1

p2<-ggplot(data=data, aes(x=Quact_3, y=Pyranometer)) +
  geom_bar(stat="identity")
p2

p3<-ggplot(data=data, aes(x=Quact_5, y=Pyranometer)) +
  geom_bar(stat="identity")
p3
```

#####  Pyranometer reading Vs degree of temperature rise

```{r, echo=TRUE}
p1<-ggplot(data=data, aes(x=TempRise_0, y=Pyranometer)) +
  geom_bar(stat="identity")
p1

p2<-ggplot(data=data, aes(x=TempRise_3, y=Pyranometer)) +
  geom_bar(stat="identity")
p2

p3<-ggplot(data=data, aes(x=TempRise_5, y=Pyranometer)) +
  geom_bar(stat="identity")
p3
```

##### Determine the best linear fit equation between Pyranometer reading and Quact

```{r, echo=TRUE}
model = lm(Pyranometer ~ Quact_0, data = data)
model

# Best Linear Fit Equation is y = 6.102x + 313.034
```

##### Plot the best linear fit

```{r, echo=TRUE}
plot(Quact_0, Pyranometer, col = "blue", pch = 20)
y_preds <- predict(model)
abline(model)
```

##### Determine the Residual Sum of Squares (RSS)

```{r, echo=TRUE}
sum(resid(model)^2)
```

##### Plot the residuals

```{r, echo=TRUE}
plot(model, 1)
plot(model, 5)
```
