---
title: "Essentials of Data Analytics"
author: "19BCE1395-Trishit Chakraborty"
date: "2/3/2022"
output:
  word_document: default
  html_document: default
subtitle: Ex-3
---

##### Reading the dataset

```{r, echo=TRUE}
data = read.csv("dataset.csv")
head(data)
View(data)
```


##### (i)Determine grand mean and mean of thermal conductivity

```{r, echo=TRUE}
attach(data)
mean(K_Analytical)
mean(K_Experimental)
mean(unique(K_Analytical))    # grand mean
mean(unique(K_Experimental))  # grand mean
```


##### (ii)Sum of Squares between and Sum of Squares within

```{r, echo=TRUE}
library(dplyr)
data <- data %>%
  rename(Vol = ï..Vol)
cor(data$Vol, data$K_Analytical)
model = lm(data$K_Analytical ~ data$Vol, data = data)
summary(model)

#finding Sum of Squares between
sumsquares_between <- sum((fitted(model) - mean(data$K_Analytical))^2)
sumsquares_between

#finding Sum of Squares within
sumsquares_within <- sum((fitted(model) - data$K_Analytical)^2)
sumsquares_within
```


##### (iii)Degrees of Freedom (Between, Within, Total)

```{r, echo=TRUE}
num_columns = 5
num_observations = 40
df_between = num_columns - 1
df_between
df_within = num_observations - num_columns
df_within
df_total = df_between + df_within
df_total
```


##### (iv)Mean Squares (Between and Within)

```{r, echo=TRUE}
meansquares_between = sumsquares_between/df_between
meansquares_between
meansquares_within = sumsquares_within/df_within
meansquares_within
```


##### (v)F_Statistic and F_Critical

```{r, echo=TRUE}
F_statistic = meansquares_between/meansquares_within
F_statistic
F_Critical = qf(p=0.05, df1=4, df2=35, lower.tail=FALSE)
F_Critical
```


##### (vi)Check, Is Null Hypothesize accepted?

```{r, echo=TRUE}
# Since F_statistic value > F_Critical value, therefore Null Hypothesis is not accepted
```


##### (vii)Plot Vol Conc Vs Thermal Conductivity

```{r, echo=TRUE}
library(ggplot2)
ggplot(data, aes(x=data$Vol, y=data$K_Analytical)) + geom_point()
ggplot(data, aes(x=data$Vol, y=data$K_Experimental)) + geom_point()
```


##### (viii)Plot Vol Conc vs % Increase in Thermal Conductivity (In Bar Chart)

```{r, echo=TRUE}
p1<-ggplot(data=data, aes(x=data$Vol, y=data$Increase_K_Analytical)) +
  geom_bar(stat="identity")
p1

p2<-ggplot(data=data, aes(x=data$Vol, y=data$Increase_K_Experimental)) +
  geom_bar(stat="identity")
p2
```


##### (ix)Error(Measured Value - Analytical Value)

```{r, echo=TRUE}
error = data$K_Experimental - data$K_Analytical
error
```