---
title: "Essentials of Data Analytics"
author: "19BCE1395-Trishit Chakraborty"
date: "2/21/2022"
output:
  word_document: default
  html_document: default
subtitle: Ex-4
---

Store Airpassengers dataset (inbuilt dataset available in ‘R’) in a dataframe named “data”, install packages such as ‘forecast’, ‘tseries’. Perform the following - 

#####  (i) Display entire dataset

```{r, echo=TRUE}
data("AirPassengers")
data = AirPassengers
data
library(forecast)
library(tseries)
```


##### (ii) Check for unfilled data 

```{r, echo=TRUE}
sum(is.na(data))
# No unfilled data is present in the dataset
```


##### (ii) Display the statistical info of the dataset such as min, max, 1st quartile, 3rd quartile, mean and median.

```{r, echo=TRUE}
summary(data)
```


##### (iii) Plot ‘data’ (No. of Air passengers Vs Year) 

```{r, echo=TRUE}
plot(data, xlab="Year", ylab = "No. of Air Passengers")
```


##### (iv) Plot as timeseries ‘data’ (monthwise) 

```{r, echo=TRUE}
boxplot(data~cycle(data),xlab="Months", ylab = "No. of Air Passengers")
```


##### (v) Decompose the data as multiplicative and store as ‘ddata’

```{r, echo=TRUE}
ddata <- decompose(data, "multiplicative")
```


##### (vi) Plot ‘ddata’

```{r, echo=TRUE}
autoplot(ddata)
```


##### (vii) Plot the following: trend, seasonal and random separately. 

```{r, echo=TRUE}
plot(ddata$seasonal)
plot(ddata$trend)
plot(ddata$random)
```


##### (viii) Perform ADF test for stationarity 

```{r, echo=TRUE}
adf.test(data) 
```


##### (ix) Plot ACF and PACF 

```{r, echo=TRUE}
MA2 <- arima.sim(n = 100, list(ma = c(0.9, 0.6)), sd = 1)
acf(MA2)
pacf(MA2)
```


##### (x) Model using ARIMA 

```{r, echo=TRUE}
arima <- auto.arima(data)
arima
```
