---
title: "Essentials of Data Analytics"
author: "19BCE1395-Trishit Chakraborty"
date: "3/1/2022"
output:
  word_document: default
  html_document: default
subtitle: Ex-5
---

#####  Loading the packages

```{r, echo=TRUE}
library(caTools)
library(ROCR)
library(dplyr)
```


#####  Reading the dataset

```{r, echo=TRUE}
data = read.csv("haberman.csv")
```


##### Renaming the columns
```{r, echo=TRUE}
data <- data %>%
  rename(x1 = X30)
data <- data %>%
  rename(x2 = X64)
data <- data %>%
  rename(x3 = X1)
data <- data %>%
  rename(y = X1.1)
```


#####  Displaying the dataset

```{r, echo=TRUE}
head(data)
View(data)
```


#####  Checking for missing values

```{r, echo=TRUE}
sum(is.na(data))
```

##### Encoding the class

```{r, echo=TRUE}
data$y[data$y == 1] = 0
data$y[data$y == 2] = 1
```


#####  Splitting dataset

```{r, echo=TRUE}
split = sample.split(data, SplitRatio = 0.8)
split
   
train = subset(data, split == "TRUE")
test = subset(data, split == "FALSE")
dim(train)
dim(test)
```


#####  Training the model

```{r, echo=TRUE}
# attach(data)
logistic_model <- glm(train$y ~ train$x1 + train$x2 + train$x3, 
                      family = binomial(link='logit'), 
                      data = train)
logistic_model
```


#####  Model Summary

```{r, echo=TRUE}
summary(logistic_model)
```


#####  Predicting the test data

```{r, echo=TRUE}
prediction <- predict(logistic_model, 
                       test, type = "response")
prediction  
```


#####  Finding the classes corresponding to the probabilites

```{r, echo=TRUE}
prediction <- ifelse(prediction > 0.5, 1, 0)
prediction
```


#####  Evaluating model accuracy using confusion matrix

```{r, echo=TRUE}
# length(prediction)
table(train$y, prediction)
   
error <- mean(prediction != train$y)
print(paste('Accuracy =', 1 - error))
```


#####  ROC-AUC Curve (Not needed)

```{r, echo=TRUE}
ROCPred <- prediction(prediction, train$y) 
ROCPer <- performance(ROCPred, measure = "tpr", 
                             x.measure = "fpr")
   
auc <- performance(ROCPred, measure = "auc")
auc <- auc@y.values[[1]]
auc
```


#####  Plotting the curve (Not needed)

```{r, echo=TRUE}
plot(ROCPer)
plot(ROCPer, colorize = TRUE, 
     print.cutoffs.at = seq(0.1, by = 0.1), 
     main = "ROC CURVE")
abline(a = 0, b = 1)
   
auc <- round(auc, 4)
legend(.6, .4, auc, title = "AUC", cex = 1)
```
